---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wrappify

<!-- badges: start -->
[![R-CMD-check](https://github.com/adityasal/DATA534_Project_G2/workflows/R-CMD-check/badge.svg)](https://github.com/adityasal/DATA534_Project_G2/actions)
<!-- badges: end -->

Wrappify is an API wrapper for the Spotify API in R. Currently, there is functionality only for the API functions which do not require access to an individuals data. 

## Installation

You can install the released version of wrappify from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wrappify")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("adityasal/DATA534_Project_G2")
```
## Example

This is a basic example that shows the intended workflow of wrappify.
We start by loading our credentials from system variables and generate an authentication token.

```{r, results='hide'}
library(wrappify)

client_id <-  Sys.getenv('CLIENT_ID')
secret_id <-  Sys.getenv('CLIENT_SECRET_ID')

getAuthenticationToken(client_id, secret_id)
```


First, we have an artist we wish to know more about. That artist is the essential alternative metal band "Ghost". We query getArtistInfo.

```{r example}
ghost <- getArtistInfo("Ghost", byName = TRUE)
ghost
```

We see that Ghost is the second artist in the list. We pull out the Spotify ID and use it to get Ghost's top songs.
```{r}
id <- ghost[2,]$id

ghostsongs <- getTopSongs(id)
ghostsongs
```

We are interested in knowing more about the song "Dance Macabre", so we pull out the song ID and use it to generate a graph of audio features.
```{r}
dance <- ghostsongs[1,]$id
getAudioFeatures(dance, output = "graph")
```
We learn that we really like Ghost, and want to get some similar artists.

```{r}
getRelatedArtists(id)
```
And now we can choose one of these artists that look interesting and learn more about them as well.

# LUKA

We may also be interested in learning about new music which fits certain metrics and genre tags

# ADITYA

Or, if we would prefer to listen to a podcast, we can use wrappify as well.

Looking for recent episodes from your favorite podcaster but can't seem to remember their ID, don't worry use `getPodcastID` to do just that.

```{r}
getPodcastID('conspiracy theory')
```


```{r}
getRecentEpisodes('5RdShpOtxKO3ZWohR2M6Sv', limit=5)
```
Fancy a shorter episode, use the duration filter and...

```{r}
getRecentEpisodes('5RdShpOtxKO3ZWohR2M6Sv', duration = 30, limit=5)
```
That should do it.

You could also check out some basic stats. In this release, you can plot the duration of episodes over time, but don't worry; we will add more functionality to this function in the future! Just enter the podcast ID and ...

```{r}
getBasicStats('5RdShpOtxKO3ZWohR2M6Sv')
```

Craving for more use our `searchForPodcast` to find a new show. How about a child-friendly Spanish podcast on history? Type in `history`, change the language to `es` and change `explicit to `FALSE`.

```{r}
searchForPodcast('history', language = 'es', market = 'ES', explicit = FALSE)
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.




