---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wrappify

<!-- badges: start -->
[![R-CMD-check](https://github.com/adityasal/DATA534_Project_G2/workflows/R-CMD-check/badge.svg)](https://github.com/adityasal/DATA534_Project_G2/actions)
[![Build Status](https://travis-ci.org/lukavuko/wrappify.svg?branch=main)](https://travis-ci.org/lukavuko/wrappify)
[![codecov](https://codecov.io/gh/lukavuko/wrappify/branch/main/graph/badge.svg?token=3XUUH12N1B)](https://codecov.io/gh/lukavuko/wrappify)
<!-- badges: end -->

Wrappify is an API wrapper for the Spotify API in R. Currently, there is functionality only for the API functions which do not require access to an individuals data. 

## Installation

You can install the released version of wrappify from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wrappify")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lukavuko/wrappify")
```
## Example 1: Obtaining Song and Artist Information

This is a basic example that shows the intended workflow of wrappify.

First, we have an artist we wish to know more about. That artist is the essential alternative metal band "Ghost". We query getArtistInfo.

```{r example}
ghost <- getArtistInfo("Ghost", byName = TRUE)
ghost
```

We see that Ghost is the second artist in the list. We pull out the Spotify ID and use it to get Ghost's top songs.
```{r}
id <- ghost[2,]$id

ghostsongs <- getTopSongs(id)
ghostsongs
```

We are interested in knowing more about the song "Dance Macabre", so we pull out the song ID and use it to generate a graph of audio features.
```{r}
dance <- ghostsongs[1,]$id
getAudioFeatures(dance, output = "graph")
```
We learn that we really like Ghost, and want to get some similar artists.

```{r}
getRelatedArtists(id)
```
And now we can choose one of these artists that look interesting and learn more about them as well.

## Example 2: Conversion of Artist/Song names to their IDs

Spotify works exclusively through object IDs, but as people of culture we know
our favourite artists, tracks, and podcasts by their names, not their IDs. As such, we
need to be able to convert these names into their IDs as seamlessly as possible.

Note that artist and track names do not need to be formatted or spelled correctly to
yield valid search results!

```{r}
# One artist, mispelled
getArtistID('sanTanana')


# Multiple artists, seamlessly
artists_of_interest <- c('alt j', 'vulfpeck', 'herbie hancock0')

do.call(rbind, lapply(artists_of_interest, getArtistID))
```

When searching for tracks you can also include artist names to narrow down
what track you're looking for!
```{r}
# Song limit defaults to 5
getTrackID('Love')

# User can increase limits
getTrackID('Love', limit = 10)

# User can search with artist name in the string for more precise results
getTrackID('Love whitney houston')
```

## Example 3: Exploring New Tracks

We may also be interested in searching for new music based on certain song metrics (danceability, energy, valence, etc.), artist styles, genre tags, and even songs themselves. For this we have the `getTrackRecommendations()` function.

Artist to ID conversion is built into the `getTrackRecommendations` function
so we can directly type names into the function.

Track to ID conversion is not yet implemented so we will use track seeds from
earlier to find new song recommendations. There seem to be some issues with
track seeds as vectors so we'll use only single tracks as our seed.

Genres can be types as a vector if wanting multiple genres. Most genre tags you
can think of exist in the Spotify API search, but in case there's no return
try using other genre names.

```{r}
# I want more songs like 'Higher Love' by Kygo and Whitney Houston
getTrackRecommendations(seed_artists = c('kygo', 'whitney houston'),
                        seed_genres = c('tropical house', 'edm'),
                        seed_tracks = '6oJ6le65B3SEqPwMRNXWjY')
```

Say we aren't satisfied with our list. We can use other parameters to better
guide Spotify's recommendation API like so:
```{r}
getTrackRecommendations(seed_artists = c('kygo', 'whitney houston'),
                        seed_genres = c('tropical house', 'edm'),
                        seed_tracks = '6oJ6le65B3SEqPwMRNXWjY',
                        limit = 12,
                        market = 'US',
                        min_popularity = 70,
                        target_valence = 1)
```
For user interest, a pie chart is provided to view what proportion of returned
content is explicit. In the future we would like to integrate optional plot
parameters, and other optional plots that can highlight song popularity and
general genre music metrics such as their energy, acousticness, liveness, and
so forth.
```{r}
getTrackRecommendations(seed_artists = c('kygo', 'whitney houston'),
                        seed_genres = c('tropical house', 'edm'),
                        seed_tracks = '6oJ6le65B3SEqPwMRNXWjY',
                        limit = 12,
                        market = 'US',
                        target_energy = 0.8,
                        target_danceability = 1,
                        target_valence = 1)
```
# ADITYA

Or, if we would prefer to listen to a podcast, we can use wrappify as well.



You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.




