---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wrappify

<!-- badges: start -->
[![R-CMD-check](https://github.com/adityasal/DATA534_Project_G2/workflows/R-CMD-check/badge.svg)](https://github.com/adityasal/DATA534_Project_G2/actions)
<!-- badges: end -->

Wrappify is an API wrapper for the Spotify API in R. Currently, there is functionality only for the API functions which do not require access to an individuals data. 

## Installation

You can install the released version of wrappify from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wrappify")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("adityasal/DATA534_Project_G2")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(wrappify)
client_id <-  Sys.getenv('CLIENT_ID')
secret_id <-  Sys.getenv('CLIENT_SECRET_ID')

get_authentication_token(client_id, secret_id)

ghost <- getArtistInfo("Ghost", byName = TRUE)
ghost
```

```{r}
id <- ghost[2,]$id

ghostsongs <- getTopSongs(id)
ghostsongs
```

```{r}
dance <- ghostsongs[1,]$id
getAudioFeatures(dance, output = "graph")
```



You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:


